---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ROptionsStrategies

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/pohnson/ROptionsStrategies.svg?branch=main)](https://travis-ci.com/pohnson/ROptionsStrategies)
<!-- badges: end -->

The goal of ROptionsStrategies is to utilize the flexibilities of R and its vast libraries to analyze options data provided through TDAmeritrade API. Although the only available strategy is short put (The Wheel,) strategies such as spread, iron condor, and butterfly are in the development roadmap.

## Installation

You can install the released version of ROptionsStrategies from [CRAN](https://CRAN.R-project.org) WHEN IT IS AVAILABLE with:

``` r
#install.packages("ROptionsStrategies") Not available yet
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pohnson/ROptionsStrategies")
```
## Authentication

The most important data point in this package is the TDAmeritrade's Consumer Key. If you haven't had one yet, please follow this thorough guideline to obtain one: <a href="https://www.reddit.com/r/algotrading/comments/c81vzq/td_ameritrade_api_access_2019_guide/">link</a>.

## Wheel_Extractor Function

Now, let's assume that you already have one and save it in a csv file. We then can read it like this.

```{r load libraries and consumer key, message=FALSE, warning=FALSE}
library(ROptionsStrategies)
library(tidyverse)

consumer_key <- read_csv("consumer_key.csv") %>% as.character()
```

Let's assume that you can only execute one Wheel trade and wonder if the option should be AMD or XLF. You can use `wheel_extractor` to get underlying data as follows:

```{r get data}
data <- wheel_extractor(
  ticker = c('AMD', 'XLF'),
  expiration_date = '2021-08-06',
  consumer_key = consumer_key,
  sleep_second = 1
)

head(data)
```

But you can also parse data from another data frame using `$`:

```{r get data from data frame}
data_ticker <- data.frame(
  ticker = c('AMD', 'XLF')
)

data2 <- wheel_extractor(
  ticker = data_ticker$ticker,
  expiration_date = '2021-08-06',
  consumer_key = consumer_key,
  sleep_second = 1
)

head(data2)
```

## Wheel Visualizer
Then you can use `wheel_visualizer` to inspect which stock at a given risk (Probability OTM) has the higest return.

```{r visualize}
wheel_visualizer(
  data = data,
  include_in_the_money = FALSE
)


```
